\chapter*{Abstract}
\thispagestyle{empty}

Given the growing demand for sustainable and efficient energy sources, electric microgrids (MGs) with direct current (DC) assume a fundamental role in decentralizing energy generation. Characterized by distributed generation and local storage, they represent an innovative benchmark in energy management. However, the implementation of DC MGs brings challenges, especially in controlling and integrating energy resources. Additionally, electric grids have evolved, becoming increasingly smarter, and have utilized advanced technologies to optimize energy efficiency and sustainability, where communication resources play a crucial role in this process, facilitating coordination and control of network elements. However, integrating these resources can also pose challenges that need to be addressed to ensure the efficient operation of DC MGs. To ensure the proper functioning of loads and minimize losses in a DC MG, it is common to use DC-DC converters. They play a fundamental role in adapting different energy sources and loads, contributing to the autonomy and reliability of electrical systems. Faced with these challenges, a sufficient condition has been proposed for the design of event-based control strategies, using a co-design approach for Buck and Boost DC-DC converters. The application of this methodology aims to reduce the number of triggered events, ensuring stability and performance of the converters.

\vspace{50pt}



\paragraph{Keywords: Microgrids, DC-DC Converters, Event-Based Control, Co-design.} 


